---
title: "Lab 6"
author: "Andrea Cornelius"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Attach packages
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank-based text example

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test)
H0: Samples drawn from populations that have equal ranks (or medians)
HA: Ranks are not equal (or medians are not equal)

### Create samples

'set.seed()' to create "pseudorandom, but reproducible samples"
Like when hiking, we all start at same mile marker.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using 'hist()'

```{r}
hist(gp_1)
hist(gp_2)
```
Try a t-test so we can compare results:

```{r}
ttest <- t.test(gp_1, gp_2)

# If these data were paired, I can just add the argument 'paired = TRUE"' within the t.test() function
# If our samples are drawn from populations w the same mean (i.e., if the null hypothesis is true), then there is a `r round(ttest$p.value,2)` the probability of finding sample means that are at least as different as the ones we drew here, by random chance. Do not reject null.
```

[A more comprehensive explanation of differences between groups...actual means, data spread, effect size, percent increase, percent change]...there is no significant difference(t(df) = t-statistic value, p = ). Don't say accept/reject hypothesis. Df = degrees of freedom, pooled sample size.

### Mann Whitney U rank-based test

We use the `wilcox.test()` function to perform a two-sample rank-based test.

```{r}
mwu <- wilcox.test(gp_1, gp_2)
```
# If our samples are drawn from populations w the same rank/median (i.e., if the null hypothesis is true), then there is a `r round(wilcox.test$p.value,2)` the probability of finding sample ranks/means that are at least as different as the ones we drew here, by random chance. Do not reject null. No significant difference in medians Mann-Whitney U.
## Simple linear regression

Two *continuous, quantitative* variables that you are trying to understand the relationship between and you think that a linear relationship makes sense. 

Use the `penguins` data from {palmerpenguins} exploring flipper length (x) versus body mass (y).
```{r}
# Use View(penguins) to look at it
# Make an exploratory scatterplot of penguin flipper length (x-axis) versus body mass (y-axis)
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm")

```
y = mx + b
body mass(g) = B1(flipper_length_mm) + B0
measurement of how diff body_mass observations are from what model line predicts it to be at that flipper_length. Ordinary least squares, sum of squares

### Find the model estimates (coefficients)

Use the `lm()` function for linear model.

Use tilde below!! "as a function of"
```{r}
penguin_lm <- lm(body_mass_g ~flipper_length_mm, data = penguins)

# Body mass (g) = 49.69(flipper_length_mm)[g/mm] - 5780.83g
# [g] = 49.69[g/mm][m]
# -5780.83g is mass of penguins with no flippers (not possible lol)
```

Model coefficients: `r penguin_lm$coefficients`
Flipper length coefficient: `r penguin_lm$coefficients[2]`
Use $ to access element lists, use [] to access individual pieces (indexing)

### Use `broom::tidy()` to get a tidy output from lm()
```{r}
penguin_lm_tidy <- tidy(penguin_lm)

penguin_lm_tidy
```
### Use broom::glance() to get output of model fit & statistical significance

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```
### Use equatiomatic::extract_eq() to return model in LaTex (LaTex is how to code math things :)

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```

### Use plot() function to automatically produce diagnostic plots

```{r}
plot(penguin_lm)
```

