---
title: "Lab 6"
author: "Andrea Cornelius"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Attach packages
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank-based text example

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test)
H0: Samples drawn from populations that have equal ranks (or medians)
HA: Ranks are not equal (or medians are not equal)

### Create samples

'set.seed()' to create "pseudorandom, but reproducible samples"
Like when hiking, we all start at same mile marker.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using 'hist()'

```{r}
hist(gp_1)
hist(gp_2)
```
Try a t-test so we can compare results:

```{r}
ttest <- t.test(gp_1, gp_2)

# If these data were paired, I can just add the argument 'paired = TRUE"' within the t.test() function
# If our samples are drawn from populations w the same mean (i.e., if the null hypothesis is true), then there is a `r round(ttest$p.value,2)` the probability of finding sample means that are at least as different as the ones we drew here, by random chance. Do not reject null.
```

[A more comprehensive explanation of differences between groups...actual means, data spread, effect size, percent increase, percent change]...there is no significant difference(t(df) = t-statistic value, p = ). Don't say accept/reject hypothesis. Df = degrees of freedom, pooled sample size.

### Mann Whitney U rank-based test

We use the `wilcox.test()` function to perform a two-sample rank-based test.

```{r}
mwu <- wilcox.test(gp_1, gp_2)
```
# If our samples are drawn from populations w the same rank/median (i.e., if the null hypothesis is true), then there is a `r round(wilcox.test$p.value,2)` the probability of finding sample ranks/means that are at least as different as the ones we drew here, by random chance. Do not reject null. No significant difference in medians (Mann-Whitney U; U = `r mwu$statistic`, p = `r round(mwu$p.value, 2)`).
The medians of group A (M = 22.4 g)  and group B (M = 31.2 g) did not differ significantly (Mannn Whitney U, ...)
